### 2021-06-07 article/main.tex
Correct probability bound for digital beamforming

\textbf {Proposition 2}
The bound
%
\Disp {
\VNm {\M {g} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {3} L \RB {\log N_{H,t} + \log N_{H,r}} ^2
}
%
holds for probability \m {p}, with
%
\Disp {
1 -p
\leq 2 \exp \SB {- \frac {9L} {\pi}} 
}

@@

To investigate \m {\VNm {\M {F} _B \V {u}} _2} (respectively for \m {\M {W} _B}), we need a large deviation result for i.i.d.\ sum of chi-square random variables \cite {LaM00}, as below.

@@

Since both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {W}_B \M {W}_R} are \m {\d_s} RIP, it does appear (if we ignore the sparsity constraint) that \m {\M {P}} has approximately \m {2\d_s} RIP.
However, it remain to show that their Kronecker product still has RIP.

@@

\textbf {Theorem 9}
Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
Then it holds that
\Disp {
\VNm {\V {d}} _2
\eqsim \mathcal {O} \SB {\R {L} \R {\log N_h}^3} 
}
for probability \m {p}, with
\Disp {
1 -p
\eqsim \mathcal {O} \SB {\mathsf {e} ^{-N_B /12}} 
}

To show this, by the definition of truncation, by \m {\ell_p} norm inequality, by Proposition 6,
\Disp {
\VNm {\M {P} _{\SB {\mathcal {AB}}}^\intercal \M {P} \V {d}} _2
\leq &\VNm {\M {P}^\intercal \M {P} \V {d}} _2 \notag \\
\leq &\R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \notag \\
\leq &2.83 \R {L} \log N_h
}
By \m {\ell_p}-norm inequality, by the definition of truncation, by Proposition 8, and by above,
\Disp {
\VNm {\V {d} _{\SB{\mathcal {A}}}} _1
\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {A}}}} _2 \notag \\
\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {AB}}}} _2 \notag \\
\leq &3.44 L \R {\log N_h}^3
+0.262 \VNm {\V {d} _{\SB{\mathcal {C}}}} _1
}
Then, substituting this and Proposition 2 above into Proposition 5, we get
\Disp {
\VNm {\V {d} _{\SB{\mathcal {C}}}} _1
\leq 5.12 L \RB {\log N_h}^2
}
Now Proposition 8 becomes
\Disp {
\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2
\leq 3.44 \R {L} \log N_h + 1.35 \R {L} \R {\log N_h} ^3
}
Finally, by plugging \m {\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2} and \m {\VNm {\V {d} _{\SB{\mathcal {C}}}} _1} into Proposition 7, we get
\Disp {
\VNm {\V {d}} _2
\leq 4.79 \R {L} \R {\log N_h}^3
}
Therefore, we set \m {\chi = \R {L} \R {\log N_h}^3}, so that \m {\VNm {\V {d}} _2 = \mathcal {O} \RB {\chi}}, as claimed.

@@

Let \m {\mathcal {R}} denote the representation of complex vectors and matrices by real vectors and matrices.
With definitions \m {\tilde {\V {y}} = \mathcal {R} \SB {\V {y}}},
\m {\tilde {\V {g}} = \mathcal {R} \SB {\V {g}}},
\m {\tilde {\M {P}} = \mathcal {R} \SB {\M {P}}},
\m {\tilde {\V {z}} = \mathcal {R} \SB {\V {z}}},
we have by construction
%
\Disp {
\V {\tilde {y}}
= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} 
}

@@

\appendices
\section{Proof of the First Zonklar Equation}
Appendix one text goes here.

\section{Proof of the First Zonklar Equation}
Appendix two text goes here.

>>>>

\textbf {Proposition 2}
The bound
\Disp {
\VNm {\M {g} _{\SB{\mathcal {C}}}} _1
\leq \frac {1} {3} L \RB {\log N_{H,t} + \log N_{H,r}} ^2
}
holds for probability \m {p}, with
\Disp {
1 -p
\leq 2 \exp \SB {- \frac {9L} {\pi}} 
}
This is proved by using Proposition 1 with triangle inequality, and bound the sample mean by Hoeffding inequality.

@@

To investigate \m {\VNm {\M {F} _B \V {u}} _2} (respectively for \m {\M {W} _B}), for \m {\V {u}} is a unit vector, we need a large deviation result for i.i.d.\ sum of chi-square random variables \cite {LaM00}, as below.

@@

Since both \m {\M {F}_B^\Tr \M {F}_R^\Tr} and \m {\M {W}_B \M {W}_R} are \m {\d_s} RIP, it does appear (if we ignore the sparsity constraint) that \m {\M {P}} has approximately \m {2\d_s} RIP.
However, it remain to show that their Kronecker product still has RIP.

@@

\textbf {Theorem 9}
Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
Then it holds that
\Disp {
\VNm {\V {d}} _2
\eqsim \mathcal {O} \SB {\R {L} \R {\log N_h}^3} 
}
for probability \m {p}, with
\Disp {
1 -p
\eqsim \mathcal {O} \SB {\mathsf {e} ^{-N_R \R {\d_s} /4}} 
}

To show this, by the definition of truncation, by \m {\ell_p} norm inequality, by Proposition 6,
\Disp {
\VNm {\M {P} _{\SB {\mathcal {AB}}}^\intercal \M {P} \V {d}} _2
\leq &\VNm {\M {P}^\intercal \M {P} \V {d}} _2 \notag \\
\leq &\R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \notag \\
\leq &2.83 \R {L} \log N_h
}
By \m {\ell_p}-norm inequality, by the definition of truncation, by Proposition 8, and by above,
\Disp {
\VNm {\V {d} _{\SB{\mathcal {A}}}} _1
\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {A}}}} _2 \notag \\
\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {AB}}}} _2 \notag \\
\leq &3.44 L \R {\log N_h}^3
+0.262 \VNm {\V {d} _{\SB{\mathcal {C}}}} _1
}
Then, substituting this and Proposition 2 above into Proposition 5, we get
\Disp {
\VNm {\V {d} _{\SB{\mathcal {C}}}} _1
\leq 5.12 L \RB {\log N_h}^2
}
Now Proposition 8 becomes
\Disp {
\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2
\leq 3.44 \R {L} \log N_h + 1.35 \R {L} \R {\log N_h} ^3
}
Finally, by plugging \m {\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2} and \m {\VNm {\V {d} _{\SB{\mathcal {C}}}} _1} into Proposition 7, we get
\Disp {
\VNm {\V {d}} _2
\leq 4.79 \R {L} \R {\log N_h}^3
}
Therefore, we set \m {\chi = \R {L} \R {\log N_h}^3}, so that \m {\VNm {\V {d}} _2 = \mathcal {O} \RB {\chi}}, as claimed.
The failure probability is taken from Proposition 3.

@@

First, complex numbers have to be recorded as the real and imaginary parts, to speed up calculation.
Let \m {\mathcal {R}} denote the representation of complex vectors and matrices by real vectors and matrices.
With definitions \m {\tilde {\V {y}} = \mathcal {R} \SB {\V {y}}},
\m {\tilde {\V {g}} = \mathcal {R} \SB {\V {g}}},
\m {\tilde {\M {P}} = \mathcal {R} \SB {\M {P}}},
\m {\tilde {\V {z}} = \mathcal {R} \SB {\V {z}}},
we have by construction
%
\Disp {
\V {\tilde {y}}
= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} 
}

@@

### 2021-06-07 treatise-context/3_2_generating_beamforming_matrices.tex
Correct probability bound for digital beamforming

Use \m {\chi _{i,j}} to denote independent complex standard normal random variables.
It follows that (respectively for \m {\M {W} _B})
%
\DispNum {C':C':WB:j2} {
\NC \VNm {\M {F} _B \V {u}} _2
=\NC \R {
   \sum _{i=0} ^{N_R-1} \VNm {\sum _{j=0} ^{N_B-1} \F {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
}
%
We need a large deviation result for i.i.d.\ sum of chi-square random variables.
To do so, we apply Lemma \m {1} in Laurent and Massart \cite [LaM00] for equal weights, with \m {x > 0} below.
By some calculation, we have the upper tail inequality (respectively for \m {\M {W} _B})
%
\DispNum {P:x:ex:ex} {
\NC \MB {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\F {x} {N_R}} + \F {2x} {N_R}}
\leq \NC \Ss {e} ^{-x} \NR
}
%
and the lower tail inequality
%
\DispNum {P:x:ex:ex!} {
\NC \MB {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\F {x} {N_R}}}
\leq \NC \Ss {e} ^{-x} \NR
}
%
With substitution \m {\d_s =16x^2 /N_B^2}, the upper tail can be simplified with \m {x <N_B}, and we get the following bound for overall failure probability.

>>>>

Use \m {\chi _{i,j}} to denote independent complex standard normal random variables.
It follows that (respectively for \m {\M {W} _B})
%
\DispNum {C':C':WB:j2} {
\NC \VNm {\M {F} _B \V {u}} _2
=\NC \R {
   \sum _{i=0} ^{N_R-1} \VNm {\sum _{j=0} ^{N_B-1} \F {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
}
%
We need a large deviation result for i.i.d.\ sum of chi-square random variables.
To do so, we apply Lemma \m {1} in Laurent and Massart \cite [LaM00] for equal weights, with \m {x > 0} below.
By some calculation, we have the upper tail inequality (respectively for \m {\M {W} _B})
%
\DispNum {P:x:ex:ex} {
\NC \MB {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\F {x} {N_R}} + \F {2x} {N_R}}
\leq \NC \Ss {e} ^{-x} \NR
}
%
and the lower tail inequality
%
\DispNum {P:x:ex:ex!} {
\NC \MB {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\F {x} {N_R}}}
\leq \NC \Ss {e} ^{-x} \NR
}
%
With substitution \m {\d_s =16x^2 /N_R^2}, the upper tail can be simplified with \m {x <N_R}, and we get the following bound for overall failure probability.

### 2021-06-07 treatise-pdflatex/3_2_generating_beamforming_matrices.tex
Correct probability bound for digital beamforming

Use \m {\chi _{i,j}} to denote independent complex standard normal random variables.
It follows that (respectively for \m {\M {W} _B})
%
\DispNum {C':C':WB:j2} {
\VNm {\M {F} _B \V {u}} _2
=\R {
   \sum _{i=0} ^{N_R-1} \VNm {\sum _{j=0} ^{N_B-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} 
}
%
We need a large deviation result for i.i.d.\ sum of chi-square random variables.
To do so, we apply Lemma \m {1} in Laurent and Massart \cite {LaM00} for equal weights, with \m {x > 0} below.
By some calculation, we have the upper tail inequality (respectively for \m {\M {W} _B})
%
\DispNum {P:x:ex:ex} {
\mathbb {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_R}} + \frac {2x} {N_R}}
\leq \mathsf {e} ^{-x} 
}
%
and the lower tail inequality
%
\DispNum {P:x:ex:ex!} {
\mathbb {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_R}}}
\leq \mathsf {e} ^{-x} 
}
%
With substitution \m {\d_s =16x^2 /N_B^2}, the upper tail can be simplified with \m {x <N_B}, and we get the following bound for overall failure probability.

>>>>

Use \m {\chi _{i,j}} to denote independent complex standard normal random variables.
It follows that (respectively for \m {\M {W} _B})
%
\DispNum {C':C':WB:j2} {
\VNm {\M {F} _B \V {u}} _2
=\R {
   \sum _{i=0} ^{N_R-1} \VNm {\sum _{j=0} ^{N_B-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} 
}
%
We need a large deviation result for i.i.d.\ sum of chi-square random variables.
To do so, we apply Lemma \m {1} in Laurent and Massart \cite {LaM00} for equal weights, with \m {x > 0} below.
By some calculation, we have the upper tail inequality (respectively for \m {\M {W} _B})
%
\DispNum {P:x:ex:ex} {
\mathbb {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_R}} + \frac {2x} {N_R}}
\leq \mathsf {e} ^{-x} 
}
%
and the lower tail inequality
%
\DispNum {P:x:ex:ex!} {
\mathbb {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_R}}}
\leq \mathsf {e} ^{-x} 
}
%
With substitution \m {\d_s =16x^2 /N_R^2}, the upper tail can be simplified with \m {x <N_R}, and we get the following bound for overall failure probability.
